### 2022-04-29 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_betacov_mapping@88087d31d74f610c94b69763691a8aafa08f8ecf 🚀
Deploying to gh-pages from @ PoisotLab/ms_betacov_mapping@434b7dd7e4792516ac36f190400a2dbd4c2c5a1e 🚀

@@

>>>>

\begin{figure}
\hypertarget{fig:richness}{%
\centering
\includegraphics{figures/combined_richness.png}
\caption{Top panel: relative diversoty of known bat hosts of
betacoronaviruses. This map shows that the region with the largest
number of possible hosts is South-Eastern Asia. Bottom panel: congruence
between the evolutionary distinctiveness of the hosts (grey to blue) and
the viruses (grey to red). By contrast to the richness map, this reveals
that South America has the most evolutionary distinct hosts \emph{and}
viruses, whereas South-Eastern Asia has mostly distinct viruses. This is
congruent with know results about New World bats being evolutionary
distinct, and suggests that they similarly have distinct
viruses.}\label{fig:richness}
}
\end{figure}

@@

\begin{figure}
\hypertarget{fig:biogeo}{%
\centering
\includegraphics{figures/combined_biogeo.png}
\caption{This is the legend of the figure\ldots{}}\label{fig:biogeo}
}
\end{figure}
